Market simulator

### 2020-10-21 analysis/05_market_simulator.Rmd
added persona reactive data for updating with imported data

# Initial persona configuration
persona_data <- read_csv(
  here::here('analysis', 'output', 'configurations', 'persona_config01.csv')
)

@@

# Follow national news
selectInput(
  "per1_national_news",
  label = "Follow national news:",
  choices = c("Rarely", "Once a week", "At least once a day"),
  # selected = "At least once a day",
  selected = ifelse(
    sum(persona_data[2:3,2]) == 0, "Rarely",
    as.character(persona_data[2:3,][which(persona_data[2:3,2] == 1), 1])
  ),
  width = "450px"
)

# Follow international news
selectInput(
  "per1_international_news",
  label = "Follow international news:",
  choices = c("Never", "Sometimes", "Always"),
  # selected = "Always",
  selected = ifelse(
    sum(persona_data[4:5,2]) == 0, "Never",
    as.character(persona_data[4:5,][which(persona_data[4:5,2] == 1), 1])
  ),
  width = "450px"
)

# Mediums to follow news
selectInput(
  "per1_news_medium",
  label = "Medium to follow news:",
  choices = c(
    "TV",
    "Print",
    "Online (not social media)",
    "Social media",
    "Radio",
    "Email newsletter",
    "News app"
  ),
  multiple = TRUE,
  # selected = c("TV", "Print", "Social media"),
  selected = deframe(persona_data[6:12,][which(persona_data[6:12,2] == 1), 1]),
  width = "450px"
)

# Follow government and public affairs
selectInput(
  "per1_follow_gov",
  label = "Follow government & public affairs:",
  choices = c("Not Often", "Often"),
  # selected = "Often",
  selected = ifelse(
    sum(persona_data[13,2]) == 0, "Not Often",
    as.character(persona_data[13,][which(persona_data[13,2] == 1), 1])
  ),
  width = "450px"
)

# Traveled to a developing country
selectInput(
  "per1_travel_developing",
  label = "Travel to developing country:",
  choices = c("Hasn't traveled to a developing country", "Traveled to a developing country"),
  # selected = "Traveled to a developing country",
  selected = ifelse(
    sum(persona_data[14,2]) == 0, "Hasn't traveled to a developing country",
    as.character(persona_data[14,][which(persona_data[14,2] == 1), 1])
  ),
  width = "450px"
)

# Liberal to Conservative
selectInput(
  "per1_political_pref",
  label = "Political views from liberal to conservative:",
  choices = c(
    "Extremely liberal",
    "Somewhat liberal",
    "Slightly liberal",
    "Moderate",
    "Slightly conservative",
    "Somewhat conservative",
    "Extremely conservative"
  ),
  # selected = "Somewhat liberal",
  selected = ifelse(
    sum(persona_data[15:20,2]) == 0, "Extremely liberal",
    as.character(persona_data[15:20,][which(persona_data[15:20,2] == 1), 1])
  ),
  width = "450px"
)

# Trust in political institutions
selectInput(
  "per1_institution_trust",
  label = "Political institution trust from none to complete:",
  choices = c(
    "No trust at all in political institutions",
    "Very little trust in political institutions",
    "Little trust in political institutions",
    "Neutral trust in political institutions",
    "Some trust in political institutions",
    "A lot of trust in political institutions",
    "Complete trust in political institutions"
  ),
  # selected = "Complete trust in political institutions",
  selected = ifelse(
    sum(persona_data[21:26,2]) == 0, "No trust at all in political institutions",
    as.character(persona_data[21:26,][which(persona_data[21:26,2] == 1), 1])
  ),
  width = "450px"
)

# People should be more charitable
selectInput(
  "per1_others_charitable",
  label = "People should be more charitable:",
  choices = c(
    "Strongly disagree",
    "Disagree",
    "Somewhat disagree",
    "Neutral",
    "Somewhat agree",
    "Agree",
    "Strongly agree"
  ),
  # selected = "Strongly agree",
  selected = ifelse(
    sum(persona_data[27:32,2]) == 0, "Strongly disagree",
    as.character(persona_data[27:32,][which(persona_data[27:32,2] == 1), 1])
  ),
  width = "450px"
)

# Religious attendance
selectInput(
  "per1_worship_attendance",
  label = "Worship service attendance:",
  choices = c(
    "Not sure",
    "Rarely attend",
    "Attend at least once a month"
  ),
  # selected = "Attend at least once a month",
  selected = ifelse(
    sum(persona_data[33:34,2]) == 0, "Not sure",
    as.character(persona_data[33:34,][which(persona_data[33:34,2] == 1), 1])
  ),
  width = "450px"
)

# Importance of religion
selectInput(
  "per1_religion_importance",
  label = "Importance of religion:",
  choices = c("Not important", "Important"),
  # selected = "Important",
  selected = ifelse(
    sum(persona_data[35,2]) == 0, "Not important",
    as.character(persona_data[35,][which(persona_data[35,2] == 1), 1])
  ),
  width = "450px"
)

# Religion
selectInput(
  "per1_religion",
  label = "Religion:",
  choices = c(
    "Catholic",
    'Protestant',
    'Christian Orthodox',
    'Jewish',
    'Muslim',
    'Sikh',
    'Hindu',
    'Buddhist',
    'Atheist',
    'Other religion'
  ),
  # selected = 'Protestant',
  selected = ifelse(
    sum(persona_data[36:44,2]) == 0, "Catholic",
    as.character(persona_data[36:44,][which(persona_data[36:44,2] == 1), 1])
  ),
  width = "450px"
)

# Importance of trusting charities
selectInput(
  "per1_charity_importance",
  label = "Charity Importance:",
  choices = c(
    "Not at all important",
    "Very unimportant",
    "Somewhat unimportant",
    "Neutral importance",
    "Somewhat important",
    "Very important",
    "Essential"
  ),
  # selected = "Somewhat unimportant",
  selected = ifelse(
    sum(persona_data[45:50,2]) == 0, "Not at all important",
    as.character(persona_data[45:50,][which(persona_data[45:50,2] == 1), 1])
  ),
  width = "450px"
)

# Trust in charities
selectInput(
  "per1_trust_in_charity",
  label = "Charity Trust:",
  choices = c(
    "No trust at all in charities",
    "Very little trust in charities",
    "Little trust in charities",
    "Neutral trust in charities",
    "Some trust in charities",
    "A lot of trust in charities",
    "Complete trust in charities"
  ),
  # selected = "Complete trust in charities",
  selected = ifelse(
    sum(persona_data[51:56,2]) == 0, "No trust at all in charities",
    as.character(persona_data[51:56,][which(persona_data[51:56,2] == 1), 1])
  ),
  width = "450px"
)

# Donation frequency
selectInput(
  "per1_donation_frequency",
  label = "Donation Frequency:",
  choices = c('Donate more than once a month, less than once a year', 'Donate at least once a month'),
  # selected = "Donate at least once a month",
  selected = ifelse(
    sum(persona_data[57,2]) == 0, "Donate more than once a month, less than once a year",
    as.character(persona_data[57,][which(persona_data[57,2] == 1), 1])
  ),
  width = "450px"
)

# Donated last year
selectInput(
  "per1_donation_amount",
  label = "Donation Amount Last Year:",
  choices = c(
    '$1-$49',
    '$50-$99',
    '$100-$499',
    '$500-$999',
    '$1,000-$4,999',
    '$5,000-$9,999',
    '$10,000+'
  ),
  # selected = "$100-$499",
  selected = ifelse(
    sum(persona_data[58:63,2]) == 0, "$1-$49",
    as.character(persona_data[58:63,][which(persona_data[58:63,2] == 1), 1])
  ),
  width = "450px"
)

# Volunteered in past 12 months
selectInput(
  "per1_volunteer_12",
  label = "Volunteered in last 12 Months:",
  choices = c("Haven't volunteered in past 12 months", "Volunteered in past 12 months"),
  # selected = "Volunteered in past 12 months",
  selected = ifelse(
    sum(persona_data[64,2]) == 0, "Haven't volunteered in past 12 months",
    as.character(persona_data[64,][which(persona_data[64,2] == 1), 1])
  ),
  width = "450px"
)

# Volunteer frequency
selectInput(
  "per1_volunteer_frequency",
  label = "Volunteer Frequency:",
  choices = c(
    "Haven't volunteered in past 12 months",
    "Rarely volunteer",
    "Volunteer more than once a month, less than once a year",
    "Volunteer at least once a month"
  ),
  # selected = "Volunteer at least once a month",
  selected = ifelse(
    sum(persona_data[65:67,2]) == 0, "Haven't volunteered in past 12 months",
    as.character(persona_data[65:67,][which(persona_data[65:67,2] == 1), 1])
  ),
  width = "450px"
)

# History of activism
selectInput(
  "per1_personal_activism",
  label = "Personal Activism:",
  choices = c('Not personally involved', 'Personally involved'),
  # selected = "Personally involved",
  selected = ifelse(
    sum(persona_data[68,2]) == 0, "Not personally involved",
    as.character(persona_data[68,][which(persona_data[68,2] == 1), 1])
  ),
  width = "450px"
)

# History of family activism
selectInput(
  "per1_family_activism",
  label = "Family Activism:",
  choices = c('Family not involved', 'Family involved'),
  # selected = "Family involved",
  selected = ifelse(
    sum(persona_data[69,2]) == 0, "Family not involved",
    as.character(persona_data[69,][which(persona_data[69,2] == 1), 1])
  ),
  width = "450px"
)

# Church or religious organization
selectInput(
  "per1_religious_member",
  label = "Church Membership:",
  choices = c("Don't belong to church",'Inactive church member', 'Active church member'),
  # selected = "Don't belong to church",
  selected = ifelse(
    sum(persona_data[70:71,2]) == 0, "Don't belong to church",
    as.character(persona_data[70:71,][which(persona_data[70:71,2] == 1), 1])
  ),
  width = "450px"
)

# Sport or recreational organization
selectInput(
  "per1_sport_member",
  label = "Sport or Recreational Membership:",
  choices = c(
    "Don't belong to sports or rec organization", 
    'Inactive sports or rec organization member',
    'Active sports or rec organization member'
  ),
  # selected = "Don't belong to sports or rec organization",
  selected = ifelse(
    sum(persona_data[72:73,2]) == 0, "Don't belong to sports or rec organization",
    as.character(persona_data[72:73,][which(persona_data[72:73,2] == 1), 1])
  ),
  width = "450px"
)

# Art, music, or educational organization
selectInput(
  "per1_art_member",
  label = "Art, Music, or Educational Membership:",
  choices = c(
    "Don't belong to educational organization",
    'Inactive art, music, or educational organization member',
    'Active art, music, or educational organization member'
  ),
  # selected = "Don't belong to educational organization",
  selected = ifelse(
    sum(persona_data[74:75,2]) == 0, "Don't belong to educational organization",
    as.character(persona_data[74:75,][which(persona_data[74:75,2] == 1), 1])
  ),
  width = "450px"
)

# Labor union
selectInput(
  "per1_labor_member",
  label = "Labor Union Membership:",
  choices = c(
    "Don't belong to union",
    'Inactive union member', 
    'Active union member'
  ),
  # selected = "Don't belong to union",
  selected = ifelse(
    sum(persona_data[76:77,2]) == 0, "Don't belong to union",
    as.character(persona_data[76:77,][which(persona_data[76:77,2] == 1), 1])
  ),
  width = "450px"
)

# Political party
selectInput(
  "per1_political_member",
  label = "Political Party Membership:",
  choices = c(
    "Don't belong to political party",
    'Inactive political party member',
    'Active political party member'
  ),
  # selected = "Active political party member",
  selected = ifelse(
    sum(persona_data[78:79,2]) == 0, "Don't belong to political party",
    as.character(persona_data[78:79,][which(persona_data[78:79,2] == 1), 1])
  ),
  width = "450px"
)

# Environmental organization
selectInput(
  "per1_environmental_member",
  label = "Environmental Organization Membership:",
  choices = c(
    "Don't belong to environmental organization",
    'Inactive environmental organization member',
    'Active environmental organization member'
  ),
  # selected = "Don't belong to environmental organization",
  selected = ifelse(
    sum(persona_data[80:81,2]) == 0, "Don't belong to environmental organization",
    as.character(persona_data[80:81,][which(persona_data[80:81,2] == 1), 1])
  ),
  width = "450px"
)

# Professional association
selectInput(
  "per1_professional_member",
  label = "Professional Association Membership:",
  choices = c(
    "Don't belong to professional association",
    'Inactive professional association member',
    'Active professional association member'
  ),
  # selected = "Don't belong to professional association",
  selected = ifelse(
    sum(persona_data[82:83,2]) == 0, "Don't belong to professional association",
    as.character(persona_data[82:83,][which(persona_data[82:83,2] == 1), 1])
  ),
  width = "450px"
)

# Humanitarian or charitable organization
selectInput(
  "per1_humanitarian_member",
  label = "Humanitarian or Charitable Organization Membership:",
  choices = c(
    "Don't belong to humanitarian or charitable organization",
    'Inactive humanitarian or charitable organization member',
    'Active humanitarian or charitable organization member'
  ),
  # selected = "Active humanitarian or charitable organization member",
  selected = ifelse(
    sum(persona_data[84:85,2]) == 0, "Don't belong to humanitarian or charitable organization",
    as.character(persona_data[84:85,][which(persona_data[84:85,2] == 1), 1])
  ),
  width = "450px"
)

# Consumer organization
selectInput(
  "per1_consumer_member",
  label = "Consumer Organization Membership:",
  choices = c(
    "Don't belong to consumer organization",
    'Inactive consumer organization member',
    'Active consumer organization member'
  ),
  # selected = "Don't belong to consumer organization",
  selected = ifelse(
    sum(persona_data[86:87,2]) == 0, "Don't belong to consumer organization",
    as.character(persona_data[86:87,][which(persona_data[86:87,2] == 1), 1])
  ),
  width = "450px"
)

# Other organization
selectInput(
  "per1_other_member",
  label = "Other Organization Membership:",
  choices = c(
    "Don't belong to another organization",
    'Inactive member in another organization',
    'Active member in another organization'
  ),
  # selected = "Don't belong to another organization",
  selected = ifelse(
    sum(persona_data[88:89,2]) == 0, "Don't belong to another organization",
    as.character(persona_data[88:89,][which(persona_data[88:89,2] == 1), 1])
  ),
  width = "450px"
)

# Gender
selectInput(
  "per1_gender",
  label = "Gender:",
  choices = c(
    "Male",
    "Female",
    "Transgender",
    "Prefer not to say",
    "Other gender"
  ),
  # selected = "Male",
  selected = ifelse(
    sum(persona_data[90:93,2]) == 0, "Male",
    as.character(persona_data[90:93,][which(persona_data[90:93,2] == 1), 1])
  ),
  width = "450px"
)

# Marital status
selectInput(
  "per1_marital_status",
  label = "Marital Status:",
  choices = c(
    "Married",
    "Widowed",
    "Divorced",
    "Separated",
    "Never married"
  ),
  # selected = "Married",
  selected = ifelse(
    sum(persona_data[94:97,2]) == 0, "Married",
    as.character(persona_data[94:97,][which(persona_data[94:97,2] == 1), 1])
  ),
  width = "450px"
)

# Education
selectInput(
  "per1_education",
  label = "Education:",
  choices = c(
    "Less than high school",
    "High school graduate",
    "Some college",
    "2 year degree",
    "4 year degree",
    "Graduate or professional degree",
    "Doctorate"
  ),
  # selected = "2 year degree",
  selected = ifelse(
    sum(persona_data[98:103,2]) == 0, "Less than high school",
    as.character(persona_data[98:103,][which(persona_data[98:103,2] == 1), 1])
  ),
  width = "450px"
)

# Income
selectInput(
  "per1_income",
  label = "Income:",
  choices = c('Less than median of $61,372', 'More than median of $61,372'),
  # selected = "More than median of $61,372",
  selected = ifelse(
    sum(persona_data[104,2]) == 0, "Less than median of $61,372",
    as.character(persona_data[104,][which(persona_data[104,2] == 1), 1])
  ),
  width = "450px"
)

# Race
selectInput(
  "per1_race",
  label = "Race:",
  choices = c(
    'White',
    'Black or African American',
    'American Indian or Alaskan Native',
    'Asian',
    'Native Hawaiian or Pacific Islander',
    'Other race'
  ),
  multiple = TRUE,
  # selected = "White",
  selected = deframe(persona_data[105:110,][which(persona_data[105:110,2] == 1), 1]),
  width = "450px"
)

# Age
selectInput(
  "per1_age",
  label = "Age:",
  choices = c('Less than median age of 36', "More than median age of 36"),
  # selected = "Less than median age of 36",
  selected = ifelse(
    sum(persona_data[111,2]) == 0, "Less than median age of 36",
    as.character(persona_data[111,][which(persona_data[111,2] == 1), 1])
  ),
  width = "450px"
)
```

>>>>

# Initial persona configuration
# persona_data <- read_csv(
#   here::here('analysis', 'output', 'configurations', 'persona_config01.csv')
# )

persona_values <- reactiveValues()

persona_data <- reactive({
  if (is.null(input$org_update$datapath)) {
    persona_data <- read_csv(here::here('analysis', 'output', 'configurations', 'persona_config01.csv'))
    # persona_values$file_name = "persona_config01.csv"
    # persona_values$file_type = "csv"
    # persona_values$file_size = file.size(here::here('analysis', 'output', 'configurations', 'persona_config01.csv'))
    # persona_values$file_path = here::here('analysis', 'output', 'configurations', 'persona_config01.csv')
  } else {
    persona_data <- read_csv(input$per_update$datapath)
    # persona_values$file_name = input$per_update$name
    # persona_values$file_size = input$per_update$size
    # persona_values$file_type = input$per_update$type
    # persona_values$file_path = input$per_update$datapath
  }
})

@@

# Follow national news
renderUI({
  per_data = persona_data()

  selectInput(
    "per1_national_news",
    label = "Follow national news:",
    choices = c("Rarely", "Once a week", "At least once a day"),
    # selected = "At least once a day",
    # selected = ifelse(
    #   sum(persona_data[2:3,2]) == 0, "Rarely",
    #   as.character(persona_data[2:3,][which(persona_data[2:3,2] == 1), 1])
    # ),
    selected = ifelse(
      sum(per_data[2:3,2]) == 0, "Rarely",
      as.character(per_data[2:3,][which(per_data[2:3,2] == 1), 1])
    ),
    width = "450px"
  )

# Follow international news
selectInput(
  "per1_international_news",
  label = "Follow international news:",
  choices = c("Never", "Sometimes", "Always"),
  # selected = "Always",
  # selected = ifelse(
  #   sum(persona_data[4:5,2]) == 0, "Never",
  #   as.character(persona_data[4:5,][which(persona_data[4:5,2] == 1), 1])
  # ),
  selected = ifelse(
    sum(per_data[4:5,2]) == 0, "Never",
    as.character(per_data[4:5,][which(per_data[4:5,2] == 1), 1])
  ),
  width = "450px"
)

# Mediums to follow news
selectInput(
  "per1_news_medium",
  label = "Medium to follow news:",
  choices = c(
    "TV",
    "Print",
    "Online (not social media)",
    "Social media",
    "Radio",
    "Email newsletter",
    "News app"
  ),
  multiple = TRUE,
  # selected = c("TV", "Print", "Social media"),
  # selected = deframe(persona_data[6:12,][which(persona_data[6:12,2] == 1), 1]),
  selected = deframe(per_data[6:12,][which(per_data[6:12,2] == 1), 1]),
  width = "450px"
)

# Follow government and public affairs
selectInput(
  "per1_follow_gov",
  label = "Follow government & public affairs:",
  choices = c("Not Often", "Often"),
  # selected = "Often",
  # selected = ifelse(
  #   sum(persona_data[13,2]) == 0, "Not Often",
  #   as.character(persona_data[13,][which(persona_data[13,2] == 1), 1])
  # ),
  selected = ifelse(
    sum(per_data[13,2]) == 0, "Not Often",
    as.character(per_data[13,][which(per_data[13,2] == 1), 1])
  ),
  width = "450px"
)

# Traveled to a developing country
selectInput(
  "per1_travel_developing",
  label = "Travel to developing country:",
  choices = c("Hasn't traveled to a developing country", "Traveled to a developing country"),
  # selected = "Traveled to a developing country",
  # selected = ifelse(
  #   sum(persona_data[14,2]) == 0, "Hasn't traveled to a developing country",
  #   as.character(persona_data[14,][which(persona_data[14,2] == 1), 1])
  # ),
  selected = ifelse(
    sum(per_data[14,2]) == 0, "Hasn't traveled to a developing country",
    as.character(per_data[14,][which(per_data[14,2] == 1), 1])
  ),
  width = "450px"
)

# Liberal to Conservative
selectInput(
  "per1_political_pref",
  label = "Political views from liberal to conservative:",
  choices = c(
    "Extremely liberal",
    "Somewhat liberal",
    "Slightly liberal",
    "Moderate",
    "Slightly conservative",
    "Somewhat conservative",
    "Extremely conservative"
  ),
  # selected = "Somewhat liberal",
  # selected = ifelse(
  #   sum(persona_data[15:20,2]) == 0, "Extremely liberal",
  #   as.character(persona_data[15:20,][which(persona_data[15:20,2] == 1), 1])
  # ),
  selected = ifelse(
    sum(per_data[15:20,2]) == 0, "Extremely liberal",
    as.character(per_data[15:20,][which(per_data[15:20,2] == 1), 1])
  ),
  width = "450px"
)

# Trust in political institutions
selectInput(
  "per1_institution_trust",
  label = "Political institution trust from none to complete:",
  choices = c(
    "No trust at all in political institutions",
    "Very little trust in political institutions",
    "Little trust in political institutions",
    "Neutral trust in political institutions",
    "Some trust in political institutions",
    "A lot of trust in political institutions",
    "Complete trust in political institutions"
  ),
  # selected = "Complete trust in political institutions",
  # selected = ifelse(
  #   sum(persona_data[21:26,2]) == 0, "No trust at all in political institutions",
  #   as.character(persona_data[21:26,][which(persona_data[21:26,2] == 1), 1])
  # ),
  selected = ifelse(
    sum(per_data[21:26,2]) == 0, "No trust at all in political institutions",
    as.character(per_data[21:26,][which(per_data[21:26,2] == 1), 1])
  ),
  width = "450px"
)

# People should be more charitable
selectInput(
  "per1_others_charitable",
  label = "People should be more charitable:",
  choices = c(
    "Strongly disagree",
    "Disagree",
    "Somewhat disagree",
    "Neutral",
    "Somewhat agree",
    "Agree",
    "Strongly agree"
  ),
  # selected = "Strongly agree",
  # selected = ifelse(
  #   sum(persona_data[27:32,2]) == 0, "Strongly disagree",
  #   as.character(persona_data[27:32,][which(persona_data[27:32,2] == 1), 1])
  # ),
  selected = ifelse(
    sum(per_data[27:32,2]) == 0, "Strongly disagree",
    as.character(per_data[27:32,][which(per_data[27:32,2] == 1), 1])
  ),
  width = "450px"
)

# Religious attendance
selectInput(
  "per1_worship_attendance",
  label = "Worship service attendance:",
  choices = c(
    "Not sure",
    "Rarely attend",
    "Attend at least once a month"
  ),
  # selected = "Attend at least once a month",
  # selected = ifelse(
  #   sum(persona_data[33:34,2]) == 0, "Not sure",
  #   as.character(persona_data[33:34,][which(persona_data[33:34,2] == 1), 1])
  # ),
  selected = ifelse(
    sum(per_data[33:34,2]) == 0, "Not sure",
    as.character(per_data[33:34,][which(per_data[33:34,2] == 1), 1])
  ),
  width = "450px"
)

# Importance of religion
selectInput(
  "per1_religion_importance",
  label = "Importance of religion:",
  choices = c("Not important", "Important"),
  # selected = "Important",
  # selected = ifelse(
  #   sum(persona_data[35,2]) == 0, "Not important",
  #   as.character(persona_data[35,][which(persona_data[35,2] == 1), 1])
  # ),
  selected = ifelse(
    sum(per_data[35,2]) == 0, "Not important",
    as.character(per_data[35,][which(per_data[35,2] == 1), 1])
  ),
  width = "450px"
)

# Religion
selectInput(
  "per1_religion",
  label = "Religion:",
  choices = c(
    "Catholic",
    'Protestant',
    'Christian Orthodox',
    'Jewish',
    'Muslim',
    'Sikh',
    'Hindu',
    'Buddhist',
    'Atheist',
    'Other religion'
  ),
  # selected = 'Protestant',
  # selected = ifelse(
  #   sum(persona_data[36:44,2]) == 0, "Catholic",
  #   as.character(persona_data[36:44,][which(persona_data[36:44,2] == 1), 1])
  # ),
   selected = ifelse(
    sum(per_data[36:44,2]) == 0, "Catholic",
    as.character(per_data[36:44,][which(per_data[36:44,2] == 1), 1])
  ),
  width = "450px"
)

# Importance of trusting charities
selectInput(
  "per1_charity_importance",
  label = "Charity Importance:",
  choices = c(
    "Not at all important",
    "Very unimportant",
    "Somewhat unimportant",
    "Neutral importance",
    "Somewhat important",
    "Very important",
    "Essential"
  ),
  # selected = "Somewhat unimportant",
  # selected = ifelse(
  #   sum(persona_data[45:50,2]) == 0, "Not at all important",
  #   as.character(persona_data[45:50,][which(persona_data[45:50,2] == 1), 1])
  # ),
  selected = ifelse(
    sum(per_data[45:50,2]) == 0, "Not at all important",
    as.character(per_data[45:50,][which(per_data[45:50,2] == 1), 1])
  ),
  width = "450px"
)

# Trust in charities
selectInput(
  "per1_trust_in_charity",
  label = "Charity Trust:",
  choices = c(
    "No trust at all in charities",
    "Very little trust in charities",
    "Little trust in charities",
    "Neutral trust in charities",
    "Some trust in charities",
    "A lot of trust in charities",
    "Complete trust in charities"
  ),
  # selected = "Complete trust in charities",
  # selected = ifelse(
  #   sum(persona_data[51:56,2]) == 0, "No trust at all in charities",
  #   as.character(persona_data[51:56,][which(persona_data[51:56,2] == 1), 1])
  # ),
   selected = ifelse(
    sum(per_data[51:56,2]) == 0, "No trust at all in charities",
    as.character(per_data[51:56,][which(per_data[51:56,2] == 1), 1])
  ),
  width = "450px"
)

# Donation frequency
selectInput(
  "per1_donation_frequency",
  label = "Donation Frequency:",
  choices = c('Donate more than once a month, less than once a year', 'Donate at least once a month'),
  # selected = "Donate at least once a month",
  # selected = ifelse(
  #   sum(persona_data[57,2]) == 0, "Donate more than once a month, less than once a year",
  #   as.character(persona_data[57,][which(persona_data[57,2] == 1), 1])
  # ),
  selected = ifelse(
    sum(per_data[57,2]) == 0, "Donate more than once a month, less than once a year",
    as.character(per_data[57,][which(per_data[57,2] == 1), 1])
  ),
  width = "450px"
)

# Donated last year
selectInput(
  "per1_donation_amount",
  label = "Donation Amount Last Year:",
  choices = c(
    '$1-$49',
    '$50-$99',
    '$100-$499',
    '$500-$999',
    '$1,000-$4,999',
    '$5,000-$9,999',
    '$10,000+'
  ),
  # selected = "$100-$499",
  # selected = ifelse(
  #   sum(persona_data[58:63,2]) == 0, "$1-$49",
  #   as.character(persona_data[58:63,][which(persona_data[58:63,2] == 1), 1])
  # ),
  selected = ifelse(
    sum(per_data[58:63,2]) == 0, "$1-$49",
    as.character(per_data[58:63,][which(per_data[58:63,2] == 1), 1])
  ),
  width = "450px"
)

# Volunteered in past 12 months
selectInput(
  "per1_volunteer_12",
  label = "Volunteered in last 12 Months:",
  choices = c("Haven't volunteered in past 12 months", "Volunteered in past 12 months"),
  # selected = "Volunteered in past 12 months",
  # selected = ifelse(
  #   sum(persona_data[64,2]) == 0, "Haven't volunteered in past 12 months",
  #   as.character(persona_data[64,][which(persona_data[64,2] == 1), 1])
  # ),
  selected = ifelse(
    sum(per_data[64,2]) == 0, "Haven't volunteered in past 12 months",
    as.character(per_data[64,][which(per_data[64,2] == 1), 1])
  ),
  width = "450px"
)

# Volunteer frequency
selectInput(
  "per1_volunteer_frequency",
  label = "Volunteer Frequency:",
  choices = c(
    "Haven't volunteered in past 12 months",
    "Rarely volunteer",
    "Volunteer more than once a month, less than once a year",
    "Volunteer at least once a month"
  ),
  # selected = "Volunteer at least once a month",
  # selected = ifelse(
  #   sum(persona_data[65:67,2]) == 0, "Haven't volunteered in past 12 months",
  #   as.character(persona_data[65:67,][which(persona_data[65:67,2] == 1), 1])
  # ),
  selected = ifelse(
    sum(per_data[65:67,2]) == 0, "Haven't volunteered in past 12 months",
    as.character(per_data[65:67,][which(per_data[65:67,2] == 1), 1])
  ),
  width = "450px"
)

# History of activism
selectInput(
  "per1_personal_activism",
  label = "Personal Activism:",
  choices = c('Not personally involved', 'Personally involved'),
  # selected = "Personally involved",
  # selected = ifelse(
  #   sum(persona_data[68,2]) == 0, "Not personally involved",
  #   as.character(persona_data[68,][which(persona_data[68,2] == 1), 1])
  # ),
  selected = ifelse(
    sum(per_data[68,2]) == 0, "Not personally involved",
    as.character(per_data[68,][which(per_data[68,2] == 1), 1])
  ),
  width = "450px"
)

# History of family activism
selectInput(
  "per1_family_activism",
  label = "Family Activism:",
  choices = c('Family not involved', 'Family involved'),
  # selected = "Family involved",
  # selected = ifelse(
  #   sum(persona_data[69,2]) == 0, "Family not involved",
  #   as.character(persona_data[69,][which(persona_data[69,2] == 1), 1])
  # ),
  selected = ifelse(
    sum(per_data[69,2]) == 0, "Family not involved",
    as.character(per_data[69,][which(per_data[69,2] == 1), 1])
  ),
  width = "450px"
)

# Church or religious organization
selectInput(
  "per1_religious_member",
  label = "Church Membership:",
  choices = c("Don't belong to church",'Inactive church member', 'Active church member'),
  # selected = "Don't belong to church",
  # selected = ifelse(
  #   sum(persona_data[70:71,2]) == 0, "Don't belong to church",
  #   as.character(persona_data[70:71,][which(persona_data[70:71,2] == 1), 1])
  # ),
  selected = ifelse(
    sum(per_data[70:71,2]) == 0, "Don't belong to church",
    as.character(per_data[70:71,][which(per_data[70:71,2] == 1), 1])
  ),
  width = "450px"
)

# Sport or recreational organization
selectInput(
  "per1_sport_member",
  label = "Sport or Recreational Membership:",
  choices = c(
    "Don't belong to sports or rec organization", 
    'Inactive sports or rec organization member',
    'Active sports or rec organization member'
  ),
  # selected = "Don't belong to sports or rec organization",
  # selected = ifelse(
  #   sum(persona_data[72:73,2]) == 0, "Don't belong to sports or rec organization",
  #   as.character(persona_data[72:73,][which(persona_data[72:73,2] == 1), 1])
  # ),
  selected = ifelse(
    sum(per_data[72:73,2]) == 0, "Don't belong to sports or rec organization",
    as.character(per_data[72:73,][which(per_data[72:73,2] == 1), 1])
  ),
  width = "450px"
)

# Art, music, or educational organization
selectInput(
  "per1_art_member",
  label = "Art, Music, or Educational Membership:",
  choices = c(
    "Don't belong to educational organization",
    'Inactive art, music, or educational organization member',
    'Active art, music, or educational organization member'
  ),
  # selected = "Don't belong to educational organization",
  # selected = ifelse(
  #   sum(persona_data[74:75,2]) == 0, "Don't belong to educational organization",
  #   as.character(persona_data[74:75,][which(persona_data[74:75,2] == 1), 1])
  # ),
  selected = ifelse(
    sum(per_data[74:75,2]) == 0, "Don't belong to educational organization",
    as.character(per_data[74:75,][which(per_data[74:75,2] == 1), 1])
  ),
  width = "450px"
)

# Labor union
selectInput(
  "per1_labor_member",
  label = "Labor Union Membership:",
  choices = c(
    "Don't belong to union",
    'Inactive union member', 
    'Active union member'
  ),
  # selected = "Don't belong to union",
  # selected = ifelse(
  #   sum(persona_data[76:77,2]) == 0, "Don't belong to union",
  #   as.character(persona_data[76:77,][which(persona_data[76:77,2] == 1), 1])
  # ),
  selected = ifelse(
    sum(per_data[76:77,2]) == 0, "Don't belong to union",
    as.character(per_data[76:77,][which(per_data[76:77,2] == 1), 1])
  ),
  width = "450px"
)

# Political party
selectInput(
  "per1_political_member",
  label = "Political Party Membership:",
  choices = c(
    "Don't belong to political party",
    'Inactive political party member',
    'Active political party member'
  ),
  # selected = "Active political party member",
  # selected = ifelse(
  #   sum(persona_data[78:79,2]) == 0, "Don't belong to political party",
  #   as.character(persona_data[78:79,][which(persona_data[78:79,2] == 1), 1])
  # ),
  selected = ifelse(
    sum(per_data[78:79,2]) == 0, "Don't belong to political party",
    as.character(per_data[78:79,][which(per_data[78:79,2] == 1), 1])
  ),
  width = "450px"
)

# Environmental organization
selectInput(
  "per1_environmental_member",
  label = "Environmental Organization Membership:",
  choices = c(
    "Don't belong to environmental organization",
    'Inactive environmental organization member',
    'Active environmental organization member'
  ),
  # selected = "Don't belong to environmental organization",
  # selected = ifelse(
  #   sum(persona_data[80:81,2]) == 0, "Don't belong to environmental organization",
  #   as.character(persona_data[80:81,][which(persona_data[80:81,2] == 1), 1])
  # ),
  selected = ifelse(
    sum(per_data[80:81,2]) == 0, "Don't belong to environmental organization",
    as.character(per_data[80:81,][which(per_data[80:81,2] == 1), 1])
  ),
  width = "450px"
)

# Professional association
selectInput(
  "per1_professional_member",
  label = "Professional Association Membership:",
  choices = c(
    "Don't belong to professional association",
    'Inactive professional association member',
    'Active professional association member'
  ),
  # selected = "Don't belong to professional association",
  # selected = ifelse(
  #   sum(persona_data[82:83,2]) == 0, "Don't belong to professional association",
  #   as.character(persona_data[82:83,][which(persona_data[82:83,2] == 1), 1])
  # ),
  selected = ifelse(
    sum(per_data[82:83,2]) == 0, "Don't belong to professional association",
    as.character(per_data[82:83,][which(per_data[82:83,2] == 1), 1])
  ),
  width = "450px"
)

# Humanitarian or charitable organization
selectInput(
  "per1_humanitarian_member",
  label = "Humanitarian or Charitable Organization Membership:",
  choices = c(
    "Don't belong to humanitarian or charitable organization",
    'Inactive humanitarian or charitable organization member',
    'Active humanitarian or charitable organization member'
  ),
  # selected = "Active humanitarian or charitable organization member",
  # selected = ifelse(
  #   sum(persona_data[84:85,2]) == 0, "Don't belong to humanitarian or charitable organization",
  #   as.character(persona_data[84:85,][which(persona_data[84:85,2] == 1), 1])
  # ),
  selected = ifelse(
    sum(per_data[84:85,2]) == 0, "Don't belong to humanitarian or charitable organization",
    as.character(per_data[84:85,][which(per_data[84:85,2] == 1), 1])
  ),
  width = "450px"
)
